---
title: "Linear Model With Predictions"
author: "Joel"
date: "2023-10-17"
output: html_document
---




Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```



## Model1
Find an equation that expresses SIMS as a function of ARM strength.

## Results

### Graphical Results

```{r}
plot(SIMS~ARM, data=data)
```

As arm strength increases, the sim score also increases. This is a positive trend in arm strength and sim score.

### Numerical Results

```{r}
cor(data$ARM, data$SIMS)
```

We have a positive correlation of 0.68 which gives a little bit of scatter. 

### Inference

```{r}
Model1 = lm(SIMS~ARM, data = data)
print(summary(Model1))
```


```{r}
plot(SIMS~ARM, data=data)
abline(Model1, col='blue')
```

The line shows the best linear fit. It shows an increase of 1 in arm strength, with sim increasing by 0.0545.


```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model1, newdata, interval= 'prediction')
```


## Model2

Find an equation that expresses SIMS as a function of GRIP strength.

## Results

### Graphical Results

```{r}
plot(SIMS~GRIP, data=data)
```

As grip strength increases, sim scores increases. There is a positve trend in grip strength to sim scores.

### Numerical Results

```{r}
cor(data$GRIP, data$SIMS)
```

There is a positive correlation of 0.63 which causes some scatter.

### Inference Results 

```{r}
Model2 = lm(SIMS~GRIP, data = data)
print(summary(Model2))
```

```{r}
plot(SIMS~GRIP, data=data)
abline(Model2, col='Red')
```

The line shows the best linear fit. It shows that there is an increase of 1 grip strength for every 0.0454 sim score.

```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model2, newdata, interval= 'prediction')
```


## Model3

Find an equation that expresses SIMS as a function of ARM and GRIP strength.

## Results

### Graphical Results

There are no graphical results for Model3 because I can't put two variables on one axis.

### Numerical Results

There are no numerical results because we have SIM as a function of two variables.

### Inference

```{r}
Model3 = lm(SIMS~ARM+GRIP, data = data)
print(summary(Model2))
```


```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model3, newdata, interval= 'prediction' ) 
```

